\documentclass{report}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}

\usepackage{charter}        % Font the for the ordinary text is Charter.
\usepackage{sourcecodepro}  % Mono spaced font for source code listings.
\usepackage{booktabs}       % For more professional looking tables.
\usepackage{listings}       % For displaying source code.
\usepackage{tabularx}       % Enables stretching table column width to fit page.
\usepackage[margin=1.2in]{geometry}
\usepackage{hyperref}

\lstset{
  basicstyle = \small\ttfamily,     % Change to small mono spaced font for source code.
  tabsize = 4,                      % Tab size used in this project.
  showlines = true,                 % Print empty lines at end of listings.
  emptylines=1,
  language = C,                     % Set C as programming language.
  frame = single,                   % Put a frame around the source code listings.
  showstringspaces = false          % Disable the the marking of spaces in strings.
}

% Make the width o of code listings a little less than half to have
% a little space between two column side by side listings.
\newcommand\codelstwidth{0.48}

% Counter for the coding rules.
% TODO rename to myRule to something more appropriate.
\newcounter{Rule}
\newcommand\codingRule{\stepcounter{Rule}Rule \theRule}

% Counter for the rules related to Doxygen.
\newcounter{DoxygenRule}
\newcommand\doxygenRule{\stepcounter{DoxygenRule}Doxygen Rule \theDoxygenRule}

\title{C Programming Style Guide}
\author{Henrik Samuelsson}

\begin{document}

\maketitle

\tableofcontents
\newpage

\chapter{Introduction}

\section{About}

\section{Terms and Definitions}

A quick reference with explanations of terms used in this document is provided in Table~\ref{tab:terms-and-defs}. Note that the definitions are often C programming language specific and might not be true in other contexts.

\begin{table}[h]
\begin{tabularx}{\textwidth}{lX}
\toprule
Term & Definition \\
\midrule
allocated storage duration & Object with dynamic storage duration, the storage is created and destroyed upon request. \\
automatic	storage duration &	Object with storage duration inside a block only, from the point of declaration to the end of the block. \\
block & A range of statements enclosed between a pair of braces. \\
declaration & Statement that introduces an identifier and its type. \\
identifier & A name given to an entity such as variables, functions, structures, et cetera. \\
object & A location in memory whose content represent a value. \\
statement & Instruction to a computer, in C typically a single line expression followed by a semicolon. \\
static storage duration & Storage duration from start to end of program execution. \\
storage duration & Determines an objects lifetime. There are three storage durations; allocated, auto, and static. \\
storage class specifier & Specifies storage duration and linkage of objects. There are five specifiers; auto, extern, register, static, and \_Thread\_local. \\
type & Variable classification such as; int, char, double, et cetera, that determines storage size and how the bit pattern stored shall be interpreted.\\
type qualifier & Adds attributes to types at the point of declaration. There are four type qualifiers; const, restrict, volatile, and \_Atomic. \\
unsafe function-like macro & A function-like macro that evaluates its argument more than once or does not evaluate it at all.

\bottomrule
\end{tabularx}
\caption{Term and definition quick reference}\label{tab:terms-and-defs}    % ChkTeX 24
\end{table}

\chapter{Rules}

\section{Strict Enumeration Initialization}

Strategy used for initialization of the members in an enum type shall be one of the following: not specifying any values, specifying all values, specifying only the first value.

\subsection{Reasoning}

Minimizes the risk that a pair of members is assigned the same value by mistake.

\noindent
\begin{minipage}[t]{\codelstwidth\linewidth}
\lstinputlisting[
	xleftmargin = 3.4pt,
	firstline = 25,
	lastline=30,
	title = {Non-Compliant}
	]{../code/main.c}
\end{minipage}
\hfill
\begin{minipage}[t]{\codelstwidth\linewidth}
\lstinputlisting[
	xrightmargin = 3.4pt,
	firstline = 4,
	lastline = 23,
	title = {Compliant}
	]{../code/main.c}
\end{minipage}

\section{No Usage of Restrict}

Do not use the restrict type qualifier.

\subsection{Reasoning}

The keyword restrict is type qualifier that can be added in a object pointer declaration. It provides a hint to the compiler that only this pointer will be used access the object. This will in some situations make it possible for the compiler to generate a more optimized result. The behavior of the code will be undefined if this guarantee is not meet. Using restrict burdens the design of the code to guarantee that the memory areas do not overlap and adds a risk, the restrict type qualifier shall hence not be used.

\subsection{Examples}

\noindent
\begin{minipage}[t]{\codelstwidth\linewidth}
\lstinputlisting[
	firstline = 40,
	lastline = 46,
	title = {Non-Compliant}
	]{../code/main.c}
\end{minipage}
\hfill
\begin{minipage}[t]{\codelstwidth\linewidth}
\lstinputlisting[
	xrightmargin = 3.4pt,
	firstline = 32,
	lastline = 38,
	title={Compliant}
	]{../code/main.c}
\end{minipage}

\input{coding-rules/rule_001_use_the_void_parameter.tex}
\input{coding-rules/rule_002_enum_for_related_constants.tex}
\input{coding-rules/rule_003_preserve_pointer_type_qualifiers.tex}
\input{coding-rules/rule-004-automatic-variable-init.tex}
\input{coding-rules/rule-005-do-nothing-define.tex}
\input{coding-rules/rule-007-no-unused-elements.tex}
\input{coding-rules/rule-009-how-to-comment-out-code.tex}
\input{coding-rules/rule-008-no-commented-out-code.tex}
\input{coding-rules/rule-010-no-logical-short-circuit-usage.tex}
\input{coding-rules/rule-011-initialize-constants.tex}
\input{coding-rules/rule-012-enum-initialization.tex}

\input{appendix-a-doxygen-usage.tex}

\end{document}
